On the performance of the MAC model

### 2018-10-30 2018_nips_vigil/smac.tex
Fixed citation

In the description below, the original MAC cell equations are shown on the \emph{left}
while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
(The equation numbering is the same as in~\cite{hudsonManning18}.)

@@

\noindent\textbf{Control unit:} 
For both models, in the control unit, the question $q$ is first transformed in each step of 
the reasoning using a \emph{position-aware}~\cite{hudsonManning18} 
linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

@@

\noindent\textbf{Read and write units:}
For both models below, $\kb_{hw}$ denotes the \emph{knowledge base}~\cite{hudsonManning18}
consisting of 3D tensors with dimension $H \times W \times d$ for each image
in the data set. The difference in computing $\kb_{hw}$ is that the simplified MAC uses
an additional linear layer on top of the 2 CNN layers present in the original MAC network.
This circumvents the need for performing additional linear transformations on the 
knowledge base, as is done by the original MAC network in \emph{each} reasoning step.

>>>>

In the description below, the original MAC cell equations are shown on the \emph{left}
while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
(The equation numbering is the same as in~\cite{hudson2018compositional}.)

@@

\noindent\textbf{Control unit:} 
For both models, in the control unit, the question $q$ is first transformed in each step of 
the reasoning using a \emph{position-aware}~\cite{hudson2018compositional} 
linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

@@

\noindent\textbf{Read and write units:}
For both models below, $\kb_{hw}$ denotes the 
\emph{knowledge base}~\cite{hudson2018compositional}
consisting of 3D tensors with dimension $H \times W \times d$ for each image
in the data set. The difference in computing $\kb_{hw}$ is that the simplified MAC uses
an additional linear layer on top of the 2 CNN layers present in the original MAC network.
This circumvents the need for performing additional linear transformations on the 
knowledge base, as is done by the original MAC network in \emph{each} reasoning step.
